---
title: "HW1_ys3508"
output: 
  github_document
---
# Problem 1
## download the package
```{r, echo = FALSE, message = FALSE}
library(tidyverse) 
```

## load the penguins dataset
```{r}
data("penguins", package = "palmerpenguins")
```

## description of the penguins dataset

the data in this dataset, including names / values of important variables；

Answer: the variables names are species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex and year
```{r}
penguins
```

the size of the dataset (using nrow and ncol)
```{r}
# Nrow/columns in penguins
x = data.frame(penguins)
nrow(x)
ncol(x)
```

the mean flipper length
```{r}
penguins %>%
  summarise(mean(flipper_length_mm, na.rm = TRUE))

# or

skimr::skim(penguins, flipper_length_mm)
```

Make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x); color points using the species variable (adding color = ... inside of aes in your ggplot code should help)
```{r}
scatterplot1 <- penguins %>%
ggplot2:::ggplot(aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point() +
ggtitle("Scatterplot of flipper_length_mm (y) vs bill_length_mm (x)") +
ylab("Flipper Length in mm") +
xlab("Bill Length in mm")

scatterplot1
```

Export scatterplot to project directory using ggsave.
```{r}
ggsave("scatterplot1.png")
```

# Problem 2

a random sample of size 10 from a standard Normal distribution
```{r}
set.seed(1234) #set seed

#random sample of size 10
samp = rnorm(10)
samp

```

create a data frame
```{r}
dataframe <- data.frame(samp)
dataframe
```

create a logical vector indicating whether elements of the sample are greater than 0
```{r}
dataframe$gt10_logic <- dataframe$samp > 0
dataframe
```

a character vector of length 10

a factor vector of length 10, with 3 different factor “levels”

