---
title: "HW1_ys3508"
output: 
  github_document
---
# Problem 1
## download the package
```{r, echo = FALSE, message = FALSE}
library(tidyverse) 
```

## load the penguins dataset
```{r}
data("penguins", package = "palmerpenguins")
```

## description of the penguins dataset

the data in this dataset, including names / values of important variables；

```{r}
tail(penguins) 
```

the size of the dataset (using nrow and ncol)
```{r}
# Nrow/columns in penguins
x = data.frame(penguins)
nrow(x)
ncol(x)
```

the mean flipper length
```{r}
penguins %>%
  summarise(mean(flipper_length_mm, na.rm = TRUE))
```

Make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x); color points using the species variable (adding color = ... inside of aes in your ggplot code should help)
```{r}
scatterplot1 <- penguins %>%
ggplot2:::ggplot(aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point() +
ggtitle("Scatterplot of flipper_length_mm (y) vs bill_length_mm (x)") +
ylab("Flipper Length in mm")+
xlab("Bill Length in mm")

scatterplot1
```




