---
title: "HW1_ys3508"
output: 
  github_document
---
# Problem 1
## Load the package and dataset
```{r, echo = FALSE, message = FALSE}
library(tidyverse) 
data("penguins", package = "palmerpenguins")
```


## Description of the penguins dataset, including names / values of important variables；

Answer: the variables names are species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex and year. The important values are in the below table.

```{r}
summary(penguins)
```

## Size of the dataset (using nrow and ncol)
```{r}
# Nrow/columns in penguins
x = data.frame(penguins)
nrow(x)
ncol(x)
```

## Mean flipper length
```{r}
penguins %>%
  summarise(mean(flipper_length_mm, na.rm = TRUE))

# or

skimr::skim(penguins, flipper_length_mm)
```

## Make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x)


```{r}
scatterplot1 <- penguins %>%
ggplot2:::ggplot(aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point() +
ggtitle("Scatterplot of flipper_length_mm (y) vs bill_length_mm (x)") +
ylab("Flipper Length in mm") +
xlab("Bill Length in mm")

scatterplot1
```

## Export scatterplot to project directory using ggsave.
```{r}
ggsave("scatterplot1.png")
```

# Problem 2

## Create a random sample of size 10 from a standard Normal distribution
```{r}
set.seed(1234) #set seed

#random sample of size 10
samp = rnorm(10)
samp

```

## Create a data frame
```{r}
dataframe <- data.frame(samp)
```

## Create a logical vector 
indicating whether elements of the sample are greater than 0
```{r}
dataframe$gt10_logic <- dataframe$samp > 0
class(dataframe$gt10_logic)
```

## Create a character vector 
Create a character vector of length 10
```{r}
dataframe$leg10_char <- vector("character", 10)
class(dataframe$leg10_char)
```

## Create a factor vector 
Create a factor vector of length 10, with 3 different factor “levels”
```{r}
dataframe$level_fact <- factor(c("low", "medium", "high", "low", "medium", "medium", "low","low","low","low"), levels = c("low", "medium", "high"))
class(dataframe$level_fact)

dataframe

```



## OR: Unsing titble to create the data frame for numeric/character/factor vector 

```{r}
dataframe2 = tibble(
  samp,
  gt10_logic = samp > 0,
  leg10_char = vector("character", 10),
  level_fact = factor(c("low", "medium", "high", "low", "medium", "medium", "low","low","low","low"), levels = c("low", "medium", "high"))
  )
dataframe2

```
## Take the mean of each variable in data frame

Answer: Character/factor vectors cannot be calculated mean, but numerical/logical vectors can.
```{r}
mean(dataframe$samp)
mean(dataframe$gt10_logic)
mean(dataframe$leg10_char)
mean(dataframe$level_fact)

```

## Convert variables from one type to another

Answer: After being converted to numeric vectors, the factor/ charactor/logical vectors  all work. When trying to take the mean, I need to make sure the vectors are numeric or logical vectors.

```{r, echo=T, results='hide'}
#convert

dataframe2$gt10_logic <- as.numeric(dataframe2$gt10_logic)
dataframe2$leg10_char <- as.numeric(dataframe2$leg10_char)
dataframe2$level_fact <- as.numeric(dataframe2$level_fact)

#check
class(dataframe2$gt10_logic)
class(dataframe2$leg10_char)
class(dataframe2$level_fact)

#mean
mean(as.numeric(dataframe2$gt10_logic))
mean(as.numeric(dataframe2$leg10_char))
mean(as.numeric(dataframe2$level_fact))

```

